Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-05-15 tex/ms.tex
updates to plotting for the linear data inference

The posterior parameter PDFs for the case of perfectly known
calibration are shown in the bottom right panels of Figure
\ref{fig:speconly_ideal}, along with the mock spectrum and posterior
samples of the mock spectrum.  In this case the observed spectrum is
the same as the intrinsic spectrum except for a distance dimming
factor, as we have assumed that the calibration vector is one
everywhere, wth no uncertainty. The PDF for stellar mass is extremely
narrow is information about the overall normalization comes from all
$\sim 3000$ spectral data points.  The single photometric data point,
with S/N of 10, adds essentially no information beyond what is
obtained from the spectrum.

Next we will \emph{not} assume that the calibration is perfectly known
and we will therefore allow the calibration parameters $\alpha$ in our
model to vary.  {\color{red} This is not converged.} In Figure
\ref{fig:speconly_calibrated} we show the result of our inference from
the spectrum and a single photometric measurement (SDSS $g$) for a
perfectly calibrated mock spectrum. To demonstrate the quality of the
fit we show both the mock input spectrum and predictions of the
observed spectra that result from several draws of the model
parameters $[\theta, \alpha]$ from posterior distribution.  We also
show samples of the inferred calibration vector,
\begin{eqnarray} \label{eq:calibration}
\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
\quad ,
\end{eqnarray}
where $\tilde{\Delta}$ is the Gaussian Process mean prediction for the
logarithmic residual between the data and the model \citep{RW}.  For the
perfectly calibrated spectrum the true calibration vector (shown in
black) is one everywhere.  The spread of the inferred calibration
vectors approximately indicates our uncertainty in the spectrophotometric
calibration when no additional calibration information is available
and only a single photometric point is available.

>>>>

The posterior parameter PDFs for the case of perfectly known
calibration are shown in the bottom right panels of Figure
\ref{fig:speconly_ideal}, along with the mock spectrum and posterior
samples of the mock spectrum.  In this case the observed spectrum is
the same as the intrinsic spectrum except for a distance dimming
factor, as we have assumed that the calibration vector is one
everywhere, wth no uncertainty. The PDF for stellar mass is extremely
narrow since information about the overall normalization comes from all
$\sim 3000$ spectral data points.  The uncertainty in stellar mass
largely reflects uncertainty in the mass-to-light ratio due to the
small uncertainties in dust, metallicity, and age given the
spectroscopic data. The single photometric data point,
with S/N of 10, adds essentially no information beyond what is
obtained from the spectrum.

Next we will \emph{not} assume that the calibration is perfectly known
and we will therefore allow the calibration parameters $\alpha$ in our
model to vary.  {\color{red} This is not converged.} In Figure
\ref{fig:speconly_calibrated} we show the result of our inference from
the spectrum and a single photometric measurement (SDSS $g$) for a
perfectly calibrated mock spectrum. To demonstrate the quality of the
fit we show both the mock input spectrum and predictions of the
observed spectra that result from several draws of the model
parameters $[\theta, \alpha]$ from posterior distribution.  We also
show samples of the inferred calibration vector,
\begin{eqnarray} \label{eq:calibration}
\frac{d}{\mu(\theta)} & = & f(\alpha) + \frac{\tilde{\Delta}}{\mu(\theta)}
\quad ,
\end{eqnarray}
where $\tilde{\Delta}$ is the Gaussian Process mean prediction for the
logarithmic residual between the data and the model \citep{RW}.  For the
perfectly calibrated spectrum the true calibration vector (shown in
black) is one everywhere.  The spread of the inferred calibration
vectors approximately indicates our uncertainty in the spectrophotometric
calibration when no additional calibration information is available
and only a single photometric point is available.
